Deliminative verbal reduplication in Mandarin Chinese

### 2024-09-09 replies-reviews.tex

Cross-linguistically, verbal reduplication in Mandarin Chinese patterns more with morphological reduplication (below as \textit{reduplication}) in other languages
than syntactic reduplication (below as \textit{repetition} \citealt[31]{Gil2005}, \citealt[1--2]{Forza2016}).
\citet[35--36]{Gil2005} considers non-iconicity and having only two copies as sufficient but not necessary conditions for reduplication.
He further proposes building one intonational group as sufficient and necessary condition for reduplication (p. 36).
All three conditions are true for verbal reduplication in Mandarin Chinese.
% one intonational group \citep[154]{Sui2018}
\citet[9]{Forza2016} argues that the substantial difference between reduplication and repetition lies in the fact that only the former affects grammatical features such as aspect.
This is also true for verbal reduplication in Mandarin Chinese.

@@

%%%%%%%%%%%%%%%%%%
\textbf{Answer:}
Since the reviewer deemed it irrelevant, the section concerning \citet{Ghomeshietal2004} is removed.

%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%
%% YL
\item p. 26, lines 24--25: ``The output reduplicates the phonology (phon) of the input verb with the possibility to have further phonological material in between. \etag indicates an underspecified list which could be empty or not''. However, it is not entirely clear what prevents phonological material other than \obj{yi} and \obj{le} to appear in between the reduplicated elements. This aspect seems to be somewhat arbitrary, and it is not evident why certain elements are permissible while others are not.

%%%%%%%%%%%%%%%%%%%%
\textbf{Answer:}
\obj{le} `\textsc{pfv}' marks the perfective aspect.
The reason for \obj{le} `\textsc{pfv}' being the only aspect marker compatible with reduplication is explained in the Section 2.3.3 concerning the semantics of the reduplication and the aspect markers.

As for \obj{yi} `one', its use stems from the historical development of delimitative verbal reduplication but is synchronically opac.
\citet[13--15]{Zhang2000} shows that delimitative verbal reduplication originates from the ``V + numeral + verbal classifier'' phrase,
where the verbal classifier is borrowed from a verb of the same form, as shown in (\ref{ex:hist1}).
\ea\label{ex:hist1}
%明又喝,岐亦喝,明连喝两喝,岐便礼拜。(《宋代卷·虚堂和尚语录》3 87 页) as cited in \citet[12]{Zhang2000}
\gll \objex{ming2} \objex{you4} \objex{he4}, \objex{qi2} \objex{yi4} \objex{he4}, \objex{ming2} \objex{lian2} \objex{he4} \objex{liang3} \objex{he4}, \objex{qi2} \objex{bian4} \objex{li3bai4}\footnotemark\\
Ming agian call Qi also call Ming in.succession call two call Qi thus bow\\
\glt `Ming called again. Qi called too. Ming called twice. Qi thus bowed.'
\z
\footnotetext{\obj{Song4dai4} \obj{juan4}: \obj{Xu1tang2} \obj{He2shang} \obj{yu3lu4} \textit{[The Song dynasty volume: Quotations from Abbot Xutang]} p. 387 as cited in \citet[12]{Zhang2000}}
Here the numeral refers to the actual number of the action taking place
and can be any number.
This evolves into the structure of V-\obj{yi}-V (or A-\obj{yi}-A), which does not express the actual number of the action anymore,
but simply conveys that the action happens in a short period of time or for only few times (\ref{ex:hist2}).
\ea\label{ex:hist2}
%且歇一歇了,去坐地。(《宋代卷·张协状元》5 19 页) as cited in \citet[13]{Zhang2000}
\gll \objex{qie3} \obj{xie1-yi-xie1} \objex{le}, \objex{qu4} \objex{zuo4} \objex{di4}.\footnotemark\\
just rest-one-rest \textsc{ptc} go sit ground\\
\glt `(Let me) just take a rest and go sit on the ground.'
\z
\footnotetext{\obj{Song4dai4} \obj{juan4}: \obj{Zhang1} \obj{Xie2} \obj{zhuang4yuan2} \textit{[The Song dynasty volume: Top graduate Zhang Xie]} p. 519 as cited in \citet[13]{Zhang2000}}
In this case, \obj{yi1} `one' cannot be replaced by other numerals.
Since V-\obj{yi}-V does not express the actual number of the action anymore,
it became possible to delete the \obj{yi1} `one',
hence the use of the VV (or AA) form, too.

@@

Synchronically, A-\obj{yi}-A has the same meaning as AA and both do not refer to the actual number of the event denoted by the verb.
This means that \obj{yi1} `one' in A-\obj{yi}-A does not contribute any specific meaning to the structure
and is only there as a historical remnant.
In this sense,  \obj{yi1} `one' appearing in between the reduplication is synchronically arbitrary. %similar to linking elements in compounds

Besides the obvious conceptual reason that  \obj{yi1} `one' is taken to mean `little, few',
there might be a phonological explanation for  \obj{yi1} `one' rather than other numerals is used in the A-\obj{yi}-A structure.
In Chinese, one form of intensifying reduplication is A-\obj{li}-AB e.g. \obj{hu2-li-hu2tu2} `confused-li-confused',
where the \obj{li} is fixed and also does not bear any meaning.
\citet[137]{Sui2018} assumes that this syllable is filled with \obj{li} because the open syllable \obj{li} is a relatively unmarked phonological constituent \citep{Yip1992}
and the second syllable in A-\obj{li}-AB occupies an unstressed position.
We can see the similarities between \obj{li} in A-\obj{li}-AB and \obj{yi} in A-\obj{yi}-A: they are both relatively unmarked and occupies an unstressed position.
This can also make it easier for  \obj{yi1} `one' rather than other numerals to become part of a fixed structure.
But a phonological account is out of the scope of this paper and has to be left for further research.

@@

The subtypes of \type{verbal-reduplication-lr} prevent phonological materials other than \phonliste{le} and \phonliste{yi} from appearing in between the reduplication by specifying what can appear in the list and what not.

%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%
%% YL
\item
The proposed analysis appears to have limitations in explaining the constraints on verbs and the observed modifications at the Aktionsart level. How can one determine which verbs are exempt from the proposed lexical rule? The proposed rule does not seem to provide a clear prediction of which verbs are allowed and which are excluded from reduplication. Why only some states and achievements are allowed? The restrictions on the usage of the progressive with reduplicated verbs also remain unexplained.
%\item
The proposed analysis appears to have a descriptive rather than an explanatory power.
%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%

%\textbf{Answer:} \itdopt{Stefan, say something. StMü: I would suggest to ignore this comment. }

%%%%%%%%%%%%%%%%%%%%%
\textbf{Answer:}
As explained in point \ref{verbclass} on page \pageref{verbclass}, we propose that verbs of all lexical aspects can be reduplicated given suitable contexts.
The incompatibility with the progressive aspect marker is explained in Section 2.3.3 concerning the semantics of the reduplication and the aspect markers.
%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%

@@

\ex%他没碰窗户，就看了玻璃一下，玻璃就烂了。(CCL)
\gll \objex{ta1} \ldots\, \objex{jiu4} \objex{kan4-le} \objex{bo1li} \objex{yi2} \objex{xia4}, \objex{bo1li} \objex{jiu4} \objex{lan4-le}.\\
he {} just look-\textsc{pfv} glass one time glass just break-\textsc{pfv}\\\jambox{(CCL)}
\glt `He just took a look at the glass and the glass just broke.'
\z
We think it has to do with the weight/length of the object, i.e. shorter objects can be placed before  \obj{yi2} \obj{xia4} `once' while longer ones cannot.
%This is not necessarily a syntactic constraint

Even if we accept that the object can be only be placed before  \obj{yi2} \obj{xia4} `once' in limited cases,
the fact that the object can be placed before  \obj{yi2} \obj{xia4} `once' in some cases but in no cases in between reduplication suggests there is a fundamental difference between the structure of the two phenomena.

%%%%%%%%%%%%%%
\item
p. 20, lines 28--31: ``\citet{Arcodiaetal2014} and \citet{BascianoMelloni2017} assumed that the first
element in the reduplication is the actual verb, which resides under \textit{init} and \textit{proc}, and that the
second element is an aspect marker, which resides in the complement position of \textit{proc}, as it delimits
the process of the event''. Based on my understanding, these authors do not claim that the second
element serves as an aspect marker. They propose that the verb and the reduplicant are the spell-out
of two copies of the same lexical item within the \textit{v}P domain: the reduplicant is the lower copy, in
complement position, and serves as an event delimiter. In this analysis, reduplication affects the Aktionsart of the verb.

%%%%%%%%%%%%%
\noindent
\textbf{Answer:} We reformulated as ``The second element is the copy of the verb, which resides in the complement position of \textit{proc} and serves as an event delimiter.''

@@

%\itdopt{St.Mü.: Did you add a footnote or is this something to be done?}
%%%%%%%%%%%%%%%%%%%%%%
\end{enumerate}

\section{Reviewer 2}\label{sec:2}
\begin{enumerate}
\item
This paper presents an innovative analysis of verb reduplication in Mandarin Chinese, demonstrating
clarity and well-organized sections. To enhance clarity, I recommend providing a brief illustration for
technical terms like LTOP, catering to readers less familiar with them.

\textbf{Answer:} These terms will be explained in detail in point \ref{ltop} on page \pageref{ltop}.

\item
The authors employ various tests to assert that verb reduplication exhibits more word-like
characteristics than phrase-like, hence justifying its morphological classification. The subsequent
adoption of a Head-Driven Phrase Structure Grammar (HPSG) framework, integrating Minimal
Recursion Semantics \citep{Copestakeetal2005}, presents advantages over prior analyses.

@@

In light of this, concluding that verb reduplication is more word-like and less phrase-like is
questionable, as regular verb phrases encounter similar challenges. Therefore, it is crucial to
explicitly justify why SVC was chosen over regular verb phrases for this comparison. Providing such
clarification will strengthen the robustness of the paper's argumentation and render the conclusion
that verb reduplication should be morphological more convincing.

For additional comments, please refer to the attached PDF file.

\textbf{Answer:}
Based on the suggestions by the reviewers and further literature research, the section on word vs. phrase is drastically revised.
The different syntactic behaviors of the reduplication and a VP are compared,
and we conclude that the behavior of the reduplication is compatible with a lexical analysis.
The comparisons with Parallel Verb Compounds and SVCs are not substantial to our arguments and are thus removed.
See the answer to Reviewer~\ref{sec:1}, point~\ref{morph} on page~\pageref{morph} for more details. 
%\itdopt{St.Mü.: This is the original review. We should say something about it. For example point to
%  explanations above or say that the issues will be taken up below when we discuss the reviewers
%  detailed comments.}

%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%
%% YL
\item
\begin{displayquote}
R2 comments on the following passage: A-\obj{kan4-kan4}
\end{displayquote}

@@

\citegen{Cheng2012} study is based on the Mandarin spoken in Taiwan.
We might assume that A-\obj{kan4-kan4} is more widely used in Taiwan than in Mainland China.
But we also found the following examples of A-\obj{kan4-kan4} in the BCC corpus \citep{BCC}, which includes mostly data from Mainland China.
This suggests that A-\obj{kan4-kan4} is acceptable for and used by at least some Mainland Chinese Mandarin speakers as well.
\ea %那么，你倒说看看 ，你会有什么样的改变\ldots \jambox{(BCC)}
\gll \objex{na4me}, \objex{ni3} \objex{dao4} \obj{shuo1-kan4-kan4}, \objex{ni3} \objex{hui4} \objex{you3} \objex{shen2meyang4de} \objex{gai3bian4}\ldots\\
then you just say-look-look you will have what.kind.of change\\\jambox{(BCC)}
\glt `Then you just try and say what kind of changes you will have.'
\z

\ea %我得听看看你的条件再说\ldots \jambox{(BCC)}
\gll \objex{wo3} \objex{dei3} \obj{ting1-kan4-kan4} \objex{ni3de} \objex{tiao2jian4} \objex{zai4} \objex{shuo1}\ldots\\
I have.to listen-look-look your condition then say\\\jambox{(BCC)}
\glt `I'll have to listen to your conditions first before talking about it/ deciding.'
\z

A statistical comparison of the acceptability and the productivity of A-\obj{kan4-kan4} among speakers of different varieties of Mandarin Chinese has to be left for future studies.

\item
\begin{displayquote}
R2 comments on the following passage: The current study will only focus on the AA, A-\textit{yi}-A, A-\textit{le}-A, A-\textit{le-yi}-A, ABAB and
AB-le-AB forms of verbal reduplication in Mandarin Chinese. AA-\textit{kan}, A-\textit{kan-kan},
AAB, A-\textit{yi}-AB, A-\textit{le}-AB will also be mentioned.
\end{displayquote}

@@

One of the key questions addressed in this paper pertains to whether verb reduplication is best understood as a morphological or a syntactic phenomenon. However, it's noteworthy that the forms emphasized in this paper are all instances of syntactic verb reduplication \citep{Xie2020}.

To further enrich the ongoing debate, I wonder whether the authors will consider the inclusion of examples that previous studies have identified as morphological verb reduplications. This addition would help demonstrate the broader scope and applicability of your analysis. Alternatively, it would be beneficial to clarify the reasons for selecting these specific forms in this article.

%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer:}
\citet{Xie2020} identifies the AABB form as morphological verb reduplication.
Even though we do not agree with \citegen{Xie2020} claim that the distinction between ABAB and AABB lies in the distinction between morphology and syntax,
we do agree that they are different grammatical processes and thus requires separate analyses (See also \citealt[Sec. 4.3]{Deng2013}, \citealt{Wang2023}).
Also note that there are numerous scholars that do consider the forms analyzed here as morphological processes (\citealt[Ch. 4]{Chao1968}, \citealt[Ch. 3]{LiThompson1981}, \citealt[4--5]{Liao2014} and \citealt[Sec. 4]{Sui2018}).
\citet[14--15]{Zhang2000} argues that the AABB form of reduplication develops from a completely separate historical origin from the AA and ABAB forms,
as the former has a intensifying rather than delimitative meaning.
\citet[83--84]{Xie2020} further points out that AABB is much less productive than ABAB.
This suggests that at least some AABB might not be formulated by rules but is stored in the lexicon as a whole.
This is probably the case for those AABBs that have an idiomatic meaning, such as \obj{zhi3-zhi3-dian3-dian3} `point-point-gesture-gesture, gossip'.
%Productively formed AABBs can be accounted for by the current analysis as the reduplication happens before the compounding process,
%i.e. monosyllabic verbs are reduplicated separately (as AA and BB respectively) and then compounded together to form AABB.
%This is in line with the proposal in \citet[Sec. 4.2]{Wang2023},
%and also explains why some AABBs do not have a base AB form, such as \textit{zou-zou-ting-ting} `walk-walk-stop-stop, walk for a while and rest for a while', *\textit{zou-ting} `walk-stop'
The current analysis has a broad scope in that it explains all forms of delimitative verbal reduplication, which previous analyses were not able to do.
An analysis for the AABB form of reduplication has to be left for further research.

@@

\itdopt{St. Mü: Können wir das nicht auch AABB? Das ist gar nicht schwer. Ich habe das für
  adverbiale Adjektive bereits implementiert. Man muss nur PHON in zwei Teile \ibox{1} und \ibox{2}
  spalten und dann eben \ibox{1} $\oplus$ \ibox{1} $\oplus$ \ibox{2} $\oplus$ \ibox{2} als PHON-Wert
nehmen. Wenn das wichtig ist, können wir das noch machen. Oder wir machen eine Fußnote hin.}

%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%
%% YL
\item
\begin{displayquote}
R2 comments on the following passage: The meaning of the reduplication is not compositional, as it does
not mean that the event denoted by the verb happens twice or multiple times, but
rather that the event happens for a short duration and/or for low frequency. This
non-compositionality suggests that a reduplication is more word-like.
\end{displayquote}

@@

I have reservations about this argument.Typically, the meaning of a phrase is constructed in a compositional manner, meaning that the individual parts contribute to the overall meaning, or it remains transparent (e.g., \citealt{Schaefer2009}). When it comes to verb reduplication, determining whether or not the meaning is transparent\slash compositional might pose a challenge. On one hand, the core meaning of a verb often remains unaltered\slash transparent even with reduplication. On the other hand, verb reduplication does introduce additional nuances, such as delimitativeness. Additionally, the authors suggest that reduplication might be compositional if it expresses a `twice or multiple times' concept, yet non-compositional if it indicates a notion of short duration. Leaving aside the question of whether `compositional' can be interpreted in this manner, it remains noteworthy that that what prior studies identified as morphological verb reduplication (AABB form) does convey a sense of repetition (or say, multiple times) and can be considered compositional. In summary, whether or not verb reduplication is compositional remains unclear.

\begin{displayquote}
R2 comments on example (26).
\end{displayquote}

@@

The key consideration here is that the unacceptability of (26b) and examples such as (2) may not hinge solely on whether part of it can be modified. Instead, it could be associated with the post-verbal placement of the adverb.

Consequently, it becomes challenging to use these examples as support for the argument that verb reduplication should be classified as a morphological rather than a syntactic phenomenon. This is because even regular verb phrases cannot be partially modified in the same manner.

%\textbf{Answer:} %Yes, this is true.

\begin{displayquote}
R2 comments on the following passage: Nothing can intervene between a Parallel Verb Compound and its subparts cannot be modified separately either (27).
\end{displayquote}

@@

Examples (27) and (28) serve as illustrations to demonstrate the application of the ``Lexical Integrity Hypothesis'' in distinguishing PVC from SVC.

In reference to (25), it is explained that the Lexical Integrity Hypothesis posits that `No
phrase-level rule may affect a proper subpart of a word.' However, it is noteworthy that the authors
employ le-insertion in (27) and (28), indicating that le- cannot be inserted into PVC but can be
inserted into SVC. This might suggest that the use of le-insertion in these examples could be
construed as a form of phrase-level operation, potentially conflicting with the author's perspective
of regarding `le' as a morphological process.

### 2024-09-09 replies-reviews.tex

\begin{displayquote}
R2 comments on the following passage:  conjunction reduction does not seem to be possible.
\end{displayquote}

@@

Regarding example (34), the conjunctive structures do not exhibit conjunction reduction, a phenomenon that typically requires a degree of overlap between two elements, as shown in (32). Example (34) presents a scenario where there is no overlap between the verb structures.

Moreover, in Mandarin, conjunctions can only be employed with nouns and not with verbs phrases or
clauses \citep{Schaefer2009}. If this holds true, it is less likely to observe conjunction reduction for
verb phrases. Consequently, it would be inappropriate to assert that verb reduplication is more
word-like and less phrase-like, as even regular verb phrases may encounter problems undergoing
conjunction reduction.

\begin{displayquote}
R2 comments on the following passage: Following the analyses above, it is clear that the reduplication failed all of the tests for phrasal status. In comparison, Parallel Verb Compounds failed all the tests as well, whereas SVCs passed all of them. This makes the behavior of the reduplication seem more similar to that of a Parallel Verb Compound than that of an SVC. Therefore, it seems more appropriate to assume reduplication to be a morphological process rather than a syntactic one.
\end{displayquote}

@@

In Section 2.4, the authors asserted that verb reduplication is more phrase-like than word-like based on its similarities with Parallel Verb Compounds as apposed to Serial Verb Construction (SVC).

However, it is crucial to acknowledge that SVC has distinctive features, some of which diverge from those of a standard verb phrase. This raises a concern that a verb phrase might not successfully pass certain tests applicable to SVC, such as the ability for a constituent to be partially modified (A regular verb phrase like `Verb + Object' cannot be partially modified by an adverb, while each verb in an SVC structure can be modified separately (28)). Therefore, when verb reduplication cannot be partially modified, asserting that it is less phrase-like solely on the basis of its differences from SVC might be inappropriate. This is because even a regular verb phrase faces limitations.

@@

%%%%%%%%%%%%%%%%%%%
\textbf{Answer:} 
See the answer to Reviewer~\ref{sec:1}, point~\ref{morph} on page~\pageref{morph} for a detailed answer.

%\itdopt{St. Mü.: We have numbers now due to enumerate. Please specify the point you are referring to exactly.}

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
%% YL
\item
\begin{displayquote}
R2 comments on the following passage: Third, idioms (43a) lose their idiomatic meaning when used with verbal classifiers (43b), but maintain their idiomatic meaning with reduplications (43c)
\end{displayquote}

@@

The reason for the loss of idiomatic meaning in (43b) but not in (43c) could be attributed to the
presence of the number `san' in (43b). If `san xia' is replaced with `yi xia,' which remains a
verbal classifier, the idiomatic meaning is perserved. In this case, there appears to be no
distinction between verbal classifier and reduplication.

%%%%%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer}:
It is not \obj{san1} \obj{xia4} `three times' that is special, but it is \obj{yi2} \obj{xia4} `once' that is special.
We can replace \obj{san1} `three' with any number above two,
and the distinction still exist.
But \obj{yi2} \obj{xia4} `once' has acquired a duration reading `for a little while' that is not available to the other event quantifiers formed by \obj{xia4}, which only have the `for X times' interpretation (\citealt[77]{Deng2013}, \citealt[16]{Zhang2000}).
We think \obj{liang3} \obj{xia4} `twice' is following this tendency, too.
In this case, it is easy to interpret \obj{yi1} \obj{xia4} and \obj{liang3} \obj{xia4} not as referring to the actual number of action taking place,
but as duration adverbials as a whole,
thus differing them from ``actual'' verbal classifier phrases with other numerals.
%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%
%% Stefan
\item
\begin{displayquote}
R2 comments on the following passage: They provided
22 the lexical rule (48) for reduplication in general, and further proposed \textit{redup-a-lr} and \textit{redup-v-lr} as subtypes of redup-type, as illustrated in (49) and (50) respectively.
\end{displayquote}

@@

It would enhance reader comprehension if the authors could provide a brief illustration of symbols
like HOOK, LTOP, IND, ARG, etc. This will aid readers in better grasping the authors' subsequent
proposals in Section 4.

\textbf{Answer:}\label{ltop}
\itdopt{Stefan}

\item
\begin{displayquote}
R2 comments on (57).
\end{displayquote}

@@

Perhaps PHON is missed in LEX-DTR of (57), even though PHON is empty in (57).

\noindent
\textbf{Answer:} PHON is not missing. The constraints regarding PHON on the mother and the daughter are coming from
another constraint. A constraint that is a subtype in the hierarchy. The type
\type{perfective-reduplication-lr} in (51), which says that the PHON value of the daughter \ibox{1} appears
twice in the PHON value of the mother with some other material ( \etag ) between the two occurrences of \ibox{1}.
%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%

@@

\item
From Pages 4 to 5, the draft provides thorough overview of the subtypes of verbal reduplication in Mandarin Chinese. Yet, I think the examples would be too heavy for now. I am not sure whether all the examples are connected to the analyses in the later sections.

\textbf{Answer:} The examples are shortened to improve readability.

\item 
In Page 7 (section 2.3.2), the draft analyzes verbal reduplication with respect to Aktionsarten. Nonetheless, I am not well-aware of the concept. The author(s) might be better to account for the concept first in more detail.

\textbf{Answer:} 
In the previous version of our paper, \textit{Aktionsart} is used to refer to the classification of lexical verbs based on their aspectual properties.
This term is first used in this sense by \citet{Agrell1908}. %78
Since the term \textit{Aktionsart} is used in different senses as well,
we now refer to this classification as verb class to avoid confusion.

Modern approaches to verb classes start with \citet{Vendler1957}, 
who proposes four verb classes: state, activity, accomplishment and achievement.
\citet{Smith1991} adds another verb class: semelfactive.
These five verb classes can be differentiated using three binary features, as shown in Table~\ref{tab:verbclass} \citep[34, 39]{XiaoMcEnery2004}.
\begin{table}
\begin{tabular}{lllll}
 \hline
 Verb class & [$\pm$ dynamic] & [$\pm$ durative] & [$\pm$ telic] & Examples\\
 \hline
 stative & $-$ & + & $-$ & know, love, believe\\
 activity & + & + & $-$ & run, walk, swim\\
 accomplishment & + & + & + & walk to school\\
 achievement & + & $-$ & + & find, reach, win\\
 semelfactive & + & $-$ & $-$ & tap, knock\\
 \hline
 \end{tabular}    
 \caption{Verb classes and their aspectual features.}
  \label{tab:verbclass}
\end{table}

@@

\textbf{Answer:} We fixed the typo.

\item
In the middle, the draft mentions the -bar derivation and be-prefixation in German. I understand the phenomenon has a similarity to verbal reduplication in Chinese. Yet, at a glance the German examples looked out-of-the-blue to me.

\textbf{Answer:} The German examples are used to illustrate the arguments that morphological processes can be productive and does not necessarily change the category or valency of the input.
To improve readability, English examples of ``-able'' derivation and ``-ed'' inflection are used instead now.

\item
The following paragraph looks terse to me. The author(s) want to provide more explanation about the four tests. In addition, the footnote 6 might be better to move into the body.
\begin{displayquote}
\citet{Duanmu1998} and \citet{Schaefer2009} proposed the following four tests to distinguish words from phrases
in Mandarin Chinese: semantic compositionality, phrasal extension, phrasal substitution and
conjunction reduction.
\end{displayquote}
